---
title: "p8105_hw6_wq2161"
author: "Wanxin Qi"
date: "11/29/2021"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(purrr)

knitr::opts_chunk$set(
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Load and clean the data for regression analysis.

```{r load_and_clean, message = FALSE}
birthweight = read_csv("data/birthweight.csv")

# Check for missing data
sum(is.na(birthweight))

birthweight = birthweight %>%
  janitor::clean_names() %>%
  mutate(
    babysex = recode(babysex, `1` = "male", `2` = "female"),
    frace = factor(frace, ordered = FALSE),
    malform = recode(malform, `0` = "absent", `1` = "present"),
    mrace = factor(mrace, ordered = FALSE)
  ) %>%
  relocate(bwt)

birthweight
```

Propose a regression model for birthweight.

```{r}
model_1 = lm(bwt ~ babysex + wtgain, data = birthweight)

birthweight %>% 
  add_residuals(model_1) %>% 
  add_predictions(model_1) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = 0, intercept = 0, color = "red") +
  labs(
    title = "Model 1 Residuals Against Fitted Values",
    x = "Fitted Values",
    y = "Residuals",
    caption = "Data From birthweight"
  )
```

I made this model by hypothesizing that birth weight is associated with baby’s sex and mother’s weight gain during pregnancy.

Compare the model to two others.

```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = birthweight)

model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = birthweight)

cv_df = crossv_mc(birthweight, 100)

cv_df =
  cv_df %>%
   mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    mod_1 = map(train, ~lm(bwt ~ babysex + wtgain, data = .x)),
    mod_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = as_tibble(.x)))) %>% 
  mutate(
    rmse_1 = map2_dbl(mod_1, test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(mod_2, test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(mod_3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(
    title = "The Average Prediction Error of Each Model",
    x = "Model",
    y = "RMSE",
    caption = "Data from birthweight"
  )
```

## Problem 2

Load the 2017 Central Park weather data.

```{r load_data, message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for est.r.squared and log(est.beta0 * est.beta1).

```{r confidence_interval, message = FALSE}
lm(tmax ~ tmin, data = weather_df) %>%
  broom::tidy()

bootstrap_rsquared =
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>%
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975)
  )

bootstrap_rsquared

bootstrap_log_betas =
  weather_df %>%
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>%
  select(.id, term, estimate) %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>%
  mutate(
    log_betas = log(`(Intercept)` * tmin)
  ) %>%
  summarize(
    ci_lower = quantile(log_betas, 0.025), 
    ci_upper = quantile(log_betas, 0.975)
  )

bootstrap_log_betas
```

